Northern Pikeminnow Predation on Juvenile Chinook Salmon in Deadwater Slough, Salmon River, Idaho and Potential Impacts to Local Populations

### 2022-01-10 analysis/paper/paper.Rmd
made a few editorial changes, and re-knit to html

---
title: "Northern Pikeminnow Predation on Juvenile Chinook Salmon in Deadwater Slough, Salmon River, Idaho and Potential Impacts to Local Populations"
author:
  - Michael W. Ackerman:
      email: mike.ackerman@mthoodenvironmental.com
      institute: [mhe_mccall, biomark]
      correspondence: true
  - Nicholas J. Porter:
      email: Nicholas.Porter@merck.com
      institute: [biomark]
      correspondence: false
  - Kevin E. See:
      email: Kevin.See@dfw.wa.gov
      institute: [biomark, wdfw]
      correspondence: false
  - Michael S. Hall:
      email: Mike.Hall1@merck.com
      institute: [biomark]
      correspondence: false
  - Tara E. Blackman:
      email: tara.blackman@mthoodenvironmental.com
      institute: [mhe_sandy]
      correspondence: false
  - Richard A. Carmichael:
      email: Richard.Carmichael@merck.com
      institute: [biomark]
      correspondence: false
institute:
  - mhe_mccall: Mount Hood Environmental, PO Box 4282, McCall, Idaho, 83638, USA
  - biomark: Biomark, Inc., 705 South 8th Street, Boise, Idaho, 83702, USA
  - wdfw: Washington Department of Fish and Wildife, Fish Program, Science Division, 1111 Washington Street NE, Olympia, Washington, 98501, USA
  - mhe_sandy: Mount Hood Environmental, 39085 Pioneer Boulevard \#100 Mezzanine, Sandy, Oregon, 97055, USA 
date: "`r format(Sys.time(), '%d %B, %Y')`"
always_allow_html: true
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      number_sections: FALSE
      toc: no
      always_allow_html: true
      fig_width: 6
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::html_document2:
      fig_caption: yes
      number_sections: FALSE
      toc: no
      fig_width: 6
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua      
fontsize: 12pt
mainfont: Times New Roman
bibliography: 
- references.bib      # Kevin's library
- AckermanLibrary.bib # Mike's library
csl: "../templates/american-fisheries-society.csl" # Insert path for the bib-style
abstract: |
keywords: |
  Northern Pikeminnow; Chinook Salmon; predation; mark-recapture; bioenergetics
highlights: |
  These are the highlights. 
---

@@

spring_abund = all_est %>%
  filter(model == "Schnabel") %>%
  select(-range, -prop_range) %>%
  inner_join(total_cpue,
             by = c("event_name", "species")) %>%
  select(species,
         model,
         model_event = event_name,
         N_F = N,
         Lci_F = Lci,
         Uci_F = Uci,
         cpue_F = catch_per_hr) %>%
  group_by(species, model) %>%
  summarise(across(c(N_F:cpue_F),
                   mean),
            .groups = "drop") %>%
    full_join(total_cpue %>%
              filter(str_detect(event_name, "Spring")) %>%
              select(species,
                     cpue_S = catch_per_hr),
            by = "species") %>%
  # calculate spring abundance estimate
  mutate(N_S = N_F * (cpue_S / cpue_F),
         Lci_S = Lci_F * (cpue_S / cpue_F),
         Uci_S = Uci_F * (cpue_S / cpue_F))

@@

```{r abund-tab}
all_est %>%
  select(-c(species, range:prop_range)) %>%
  rename(`Effort` = event_name,
         Estimator = model,
         `L CI` = Lci,
         `U CI` = Uci) %>%
  kable(booktabs = T,
        format.args = list(big.mark = ","),
        caption = "Point estimates, standard errors, and 95% confidence intervals for each of the mark-recapture estimators and for the fall sampling efforts. Standard errors are not available for the multiple-census estimators.") %>%
  kable_styling()

>>>>

---
title: "Northern Pikeminnow Predation on Juvenile Chinook Salmon in Deadwater Slough, Salmon River, Idaho and Potential Impacts to Local Populations"
author:
  - Michael W. Ackerman:
      email: mike.ackerman@mthoodenvironmental.com
      institute: [mhe_mccall, biomark]
      correspondence: true
  - Nicholas J. Porter:
      email: Nicholas.Porter@merck.com
      institute: [biomark]
      correspondence: false
  - Kevin E. See:
      email: Kevin.See@dfw.wa.gov
      institute: [biomark, wdfw]
      correspondence: false
  - Michael S. Hall:
      email: Mike.Hall1@merck.com
      institute: [biomark]
      correspondence: false
  - Tara E. Blackman:
      email: tara.blackman@mthoodenvironmental.com
      institute: [mhe_sandy]
      correspondence: false
  - Richard A. Carmichael:
      email: Richard.Carmichael@merck.com
      institute: [biomark]
      correspondence: false
institute:
  - mhe_mccall: Mount Hood Environmental, PO Box 4282, McCall, Idaho, 83638, USA
  - biomark: Biomark, Inc., 705 South 8th Street, Boise, Idaho, 83702, USA
  - wdfw: Washington Department of Fish and Wildife, Fish Program, Science Division, 1111 Washington Street NE, Olympia, Washington, 98501, USA
  - mhe_sandy: Mount Hood Environmental, 39085 Pioneer Boulevard \#100 Mezzanine, Sandy, Oregon, 97055, USA 
date: "`r format(Sys.time(), '%d %B, %Y')`"
always_allow_html: true
output: 
    bookdown::html_document2:
      fig_caption: yes
      number_sections: FALSE
      toc: no
      fig_width: 6
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua      
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      number_sections: FALSE
      toc: no
      always_allow_html: true
      fig_width: 6
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
fontsize: 12pt
mainfont: Times New Roman
bibliography: 
- references.bib      # Kevin's library
- AckermanLibrary.bib # Mike's library
csl: "../templates/american-fisheries-society.csl" # Insert path for the bib-style
abstract: |
keywords: |
  Northern Pikeminnow; Chinook Salmon; predation; mark-recapture; bioenergetics
highlights: |
  These are the highlights. 
---

@@

spring_abund = all_est %>%
  filter(model == "Schnabel") %>%
  # filter(model == "Chapman") %>%
  select(-range, -prop_range) %>%
  inner_join(total_cpue,
             by = c("event_name", "species")) %>%
  select(species,
         model,
         model_event = event_name,
         N_F = N,
         Lci_F = Lci,
         Uci_F = Uci,
         cpue_F = catch_per_hr) %>%
  group_by(species, model) %>%
  summarise(across(c(N_F:cpue_F),
                   mean),
            .groups = "drop") %>%
    full_join(total_cpue %>%
              filter(str_detect(event_name, "Spring")) %>%
              select(species,
                     cpue_S = catch_per_hr),
            by = "species") %>%
  # calculate spring abundance estimate
  mutate(N_S = N_F * (cpue_S / cpue_F),
         Lci_S = Lci_F * (cpue_S / cpue_F),
         Uci_S = Uci_F * (cpue_S / cpue_F))

@@

```{r abund-tab}
all_est %>%
  mutate(across(c(N, SE, Lci, Uci),
                ~ prettyNum(round(.), big.mark = ","))) %>%
  rowwise() %>%
  mutate(CI = paste(Lci, Uci,
                    sep = " - ")) %>%
  select(-c(species, range:prop_range),
         -Lci, -Uci) %>%
  rename(`Effort` = event_name,
         Estimator = model,
         `95% Confidence Interval` = CI) %>%
         # `L CI` = Lci,
         # `U CI` = Uci) %>%
  kable(booktabs = T,
        format.args = list(big.mark = ","),
        caption = "Point estimates, standard errors, and 95% confidence intervals for each of the mark-recapture estimators and for the fall sampling efforts. Standard errors are not available for the multiple-census estimators.") %>%
  kable_styling()
